### 2021-11-24 input/proposal.tex
better plan?

Algorithm~\ref{algo:add} shows the instructions that implement
forwarding of best to reach consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values piggybacked in messages and
  accumulated over forwarding,
\item \processes only add new partitions to the system,
\item and \processes never join, crash nor leave the system.
\end{inparaenum}
For the sake of simplicity and to remove obvious loops, a \process
does not forward a notification to its sender
(Line~\ref{line:accumulator}).  Figure~\ref{fig:add} illustrates the
behavior of this algorithm on a system comprising 4 \processes $a$,
$b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
their partition.  They \NAMEB a notification \underline{a}dd message:
$\alpha_a^0$ and $\alpha_d^0$. They initialize their own state with
the lowest possible bound $0$ (see Line~\ref{line:lowestbound}), and
send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, \Process~$b$ receives $\alpha_{d}^{1}$. Since
it improves its own partition distance, it keeps it and forwards it to
its neighbors. In Figure~\ref{fig:addD}, \Process~$b$ discards
$\alpha_{a}^{2}$, for it does not improve its partition
distance. \Processes $c$ and $d$ will never acknowledge that
Source~$a$ exists. Ultimately, \processes discard last transiting
messages. Despite the obvious lack of traffic optimization, the system
reaches consistent partitioning.

@@

@@

\input{input/figsimplerproblem.tex}

@@

\begin{definition}[\label{def:echo}\underline{E}chos (E)]
  A \process $x$ that receives a stale message sends back --~or
  echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'})$ with
  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in D_x$.
\end{definition}

\begin{lemma}[\label{def:fbfse}FB+FS+E $\centernot\implies$ DCP]
  Forwarding of best up-to-date, forwarding of staleness, and echos is
  not sufficient to guarantee dynamic consistent partitioning.
\end{lemma}

\begin{proof}
Stale control information as stated in Definition~\ref{def:lwo} may
impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} depicts a scenario comprising only three
\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
receive the messages in the order of their sending ($s_{pq}(m)
\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
$\alpha_c^1$, for it improves its best partition. Then it receives and
discards $\delta_a$, for its best partition does not match the deleted
one. We simplify the echo since $\alpha_c^3$ is already transiting
towards $a$. Finally, Figure~\ref{fig:problemD} shows that eventually,
$c$ stays in the deleted partition $P_a$ for not having received
$\delta_a$ that $b$ blocked earlier. \end{proof}

As a cascading effect, in Figure~\ref{fig:problemD}, not only $c$
wrongfully believes that it belongs to $a$'s partition when $a$
already deleted it, but it could contribute to its inconsistency by
blocking farther but up-to-date messages from actual sources. To reach
consistent partitioning, \processes need
\begin{inparaenum}[(i)]
\item to detect possibly blocking conditions 
\item to purge all stale messages from the system
\item enabling up-to-date notifications to eventually reach every
  \process.
\end{inparaenum}

\begin{lemma}[\label{def:detection}Detector existence]
  Assuming a chain of \process $[x,\ldots, z]$ that delivered a
  message $\alpha_x$, if $x$ deletes its partition, either all
  \processes eventually deliver $\delta_s$, or a \process along the
  chain detects the blocking of the delete notification
\end{lemma}

\TODO{But cannot just delete. It must be deleted only downstream, see
  figure.}

\begin{definition}[\label{def:purge}Message purge]
  A system \underline{p}urges a message when every \node $q$ that
  delivered $m$ eventually delivers another message $m'$ never
  followed by the delivery of the former message $m$:
  $d_q(m) \implies \exists m': \eventually (d_q(m) \rightarrow d_q(m')
  \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
\end{definition}

\begin{lemma}[FB $\wedge$ FD $\implies$ Detection] \TODO{meow!}
\end{lemma}

\begin{definition}[\TODO{Assuming purge, echo => DCP}]
\end{definition}

\TODO{rest to rework\ldots}

\begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
    \underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
%
  When a \process can \texttt{Add} and \texttt{Del}ete its partition,
  to ensure consistent partitioning, eventual forwarding of best
  (Theorem~\ref{theo:efb}) additionally requires
\begin{inparaenum}[(i)]
\item eventual purging of stale messages ($\mathcal{S}(m) \implies
  \mathcal{P}(m)$), then
\item the eventual forwarding of best (Theorem~\ref{theo:efb}).
\end{inparaenum}
\end{theorem}

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] A \process may receive messages in such
    an order (\eg in Figure~\ref{fig:problemC}: $d_b(\alpha_c^1)
    \rightarrow r_b(\delta_a) \rightarrow r_b(\delta_a)$) that it does
    not forward messages required by other \processes ($\delta_a$ for
    $c$). The last delivery of some nodes may be wrong (\eg in
    Figure~\ref{fig:problemD}: $\alpha_a^3$ instead of $\delta_a$).
    % \Processes never
    % reach consistent partitioning.
    %
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
    \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, a \process may
    never end up in its best partition.
    %    Therefore, \processes do not reach
    % consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process ($S(\alpha_a) \implies
    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
    removal eventually triggers the forwarding of best delivered
    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
    \processes may deliver other stale messages that will be 
    eventually removed to never be delivered again. In the worst case,
    all \processes deliver and remove all stale messages to ultimately
    deliver and forward only up-to-date messages ($\eventually d_c(m')
    \implies \neg S(m')$). As in Theorem~\ref{theo:efb}, they
    eventually deliver and forward their best up-to-date message.

    %% upon receipt of such $\alpha_y$, either the \process already
    %% delivered its removal and it does

    %% ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
    %% S(\alpha_y)$)

    %% eventually every \process only delivers and forwards up-to-date
    %% messages, or no message at all

    %% , every \process eventually delivers and forwards the best
    %% up-to-date delivered messages as in Theorem~\ref{theo:bef}.

    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
  Using EFB$^+$, \processes reach consistent partitioning together
  even under dynamic partitioning settings where \nodes can
  \texttt{Add} and \texttt{Del}ete their partition.
\end{proof}

@@

The main challenge consists in implementing a purging mechanism that
ensures the \emph{eventual and definitive} removal of stale control
information. One could guarantee consistent partitioning by always
propagating the $\delta$ messages corresponding to the $\alpha$
messages it propagated before. In Figure~\ref{fig:problem}, it means
that as soon as \Process~$b$ forwards $\alpha_a^2$, it assumes that
its neighbors \Process~$c$ and \Process~$d$ may need the notification
of removal $\delta_a$ if it exists. However, such a solution also
implies that \processes generate traffic not only related to their
current partition, but also related to partitions they belonged to in
the past. This would prove overly expensive in dynamic systems where
\processes join and leave the system, create and delete partitions, at
any time.  Instead, we propose to use the delivery order at each
\process to detect possible inconsistencies and solve them.
%% Together, \processes eventually remove all stale control information
%% (transiting messages and local states) of the system leaving room for
%% propagation of messages about up-to-date partitions.

@@

\begin{theorem}[\label{theo:threephase}Three-phase purge]
  Three phases are sufficient to eventually purge the system from
  stale control information:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocked deletion, and
  \item propagation of delete notifications that were possibly blocked.
  \end{inparaenum}
\end{theorem}

@@

\begin{proof}
  We must prove that every \process that delivered a stale $\alpha_X$
  eventually delivers a better $\alpha_Y$, or delivers a removal
  notification of $\alpha_X$.  Figure~\ref{fig:proofB} summarizes the
  issue of purging in scenarios involving concurrent operations.

  (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
  but whose parent is neither inconsistent (like $b$) nor receiving
  $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
  \process, either directly or transitively, for such a child \process
  ($d$) trusts the possible removal of $P_X$ by delivering and
  forwarding such $\Delta$. $\Delta$ suffers from identical blocking
  conditions (between $b$ and $c$) than $\delta$, leading to the same
  solutions of detection and propagation of $\Delta$. Eventually,
  every \process whose last delivery is $\alpha_X$ receives and
  delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
  %
  %% Some \processes may have delivered messages about other partitions
  %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
  %% messages about $P_Y$.  For \processes such as $b$, the last delivery
  %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
  %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
  %% as $c$, the last delivery is $\alpha_X$, and they delivered the
  %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
  %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
  %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
  %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
  %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
  %% the chain: $d$ is a child of \processes that delivered messages
  %% about $P_Y$.
  %
  %% \begin{asparadesc}
  %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
  %%   like $a$.  By propagating from \process to \process the
  %%   corresponding $\delta_X$ message, these \processes purge
  %%   $\alpha_X$.
  %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
  %%   latter does not target its current partition.
  %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
  %%   that $[a, b, c, d]$ is solved and that it does not require to
  %%   purge $P_Y$.}
  %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
  %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
  %%   it detects $b$ is its parent, and possibly blocked any delta with
  %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
  %%   sure, $\Delta$
  %
  %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
  %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
  %%   \Process~$b$ that do not directly suffer from the non-delivery of
  %%   $\delta_X$. They need to purge their own $P_Y$ if need
  %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
  %%   one following \process will receive.
  %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
  %%   such as \Process~$c$ that do not belong to the preceding category,
  %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
  %%   forwarding guarantees that they receive $\alpha_Y$, which
  %%   contradicts their history or state. In such a case, the detecting
  %%   \processes purge their own $\alpha_X$. The detecting \processes
  %%   must also notify subsequent \processes that their current
  %%   partition \emph{may be} deleted. Indeed their parent may have
  %%   blocked the corresponding $\delta$ messages and subsequent
  %%   \processes must purge their possibly stale state, for the sake of
  %%   consistency.  We note such a notification $\Delta_X$ to emphasize
  %%   their proximity to $\delta_X$ messages.
  %%   % the uncertainty of a $\delta$ message.
  %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
  %%   their parent:] \Processes such as \Process~$d$ that have
  %%   $\alpha_X$ but preceding delivered messages are not
  %%   important. Such \processes must trust detecting \processes by
  %%   delivering and forwarding $\Delta_X$. It is worth noting that
  %%   these messages are subject to all aforementioned blocking
  %%   conditions, but are also solved by aforementioned mechanisms.
  %% \end{asparadesc}
  %% Propagation~I terminates: a \process does not deliver a $\delta$
  %% message if it has already delivered it. Propagation~III terminates: a
  %% \process does not deliver a looping message.  
  % ; and since \processes forward the messages they deliver, upstream
  % \processes eventually receive and may deliver messages detected as
  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
  % receives $\delta_f$ from \Process~$b'$.
  %% Three-phase purge ensures that all \processes of the system
  %% eventually removes stale messages, leaving room for best eventual
  %% forwarding of up-to-date messages.
  %
  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
  % delete to $e$, it will solve the inconsistency.}
  %
  %% In the meantime, \processes that still belong to a partition can
  %% propagate their respective last $\alpha$ message, and reach
    %% consistent partitioning.
\end{proof}

>>>>

Algorithm~\ref{algo:add} shows the instructions that implement
forwarding of best to reach consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values piggybacked in messages and
  accumulated over forwarding,
\item \processes only add new partitions to the system,
\item and \processes never join, crash nor leave the system.
\end{inparaenum}
For the sake of simplicity and to remove obvious loops, a \process
does not forward a notification to its sender
(Line~\ref{line:accumulator}).  Figure~\ref{fig:add} illustrates the
behavior of this algorithm on a system comprising 4 \processes $a$,
$b$, $c$, and $d$. \Process~$a$ and \Process~$d$ become the sources of
their partition.  They \NAMEB a notification \TODO{\underline{a}dd
  message}: $\alpha_a^0$ and $\alpha_d^0$. They initialize their own
state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, \Process~$b$
receives $\alpha_{d}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. In
Figure~\ref{fig:addD}, $b$ discards $\alpha_{a}^{2}$, for it does not
improve its partition distance. \Processes $c$ and $d$ will never
acknowledge that Source~$a$ exists. Ultimately, \processes discard
last transiting messages. Despite the obvious lack of traffic
optimization, the system reaches consistent partitioning.

@@

\input{input/figsimplerproblem.tex} %% positioning

@@

@@

\begin{definition}[\label{def:echo}FB$^+$: echos] FB where a
  \process $x$ that receives a stale message sends back --~or
  echoes~-- its best up-to-date delivered message: $r_{xy}(\alpha_s)
  \wedge \delta_s \in D_x \implies s_{xy}(\alpha_{s'})$ with
  $\alpha_{s'} = \min D_x \wedge \delta_{s'} \not\in D_x$.
\end{definition}

\begin{lemma}[\label{def:fbfse}FB$^+ \wedge$ FS $\centernot\implies$ DCP]
  Forwarding best up-to-date, forwarding staleness, and echoing is not
  sufficient to guarantee dynamic consistent partitioning.
\end{lemma}

\begin{proof}
Stale control information as stated in Definition~\ref{def:lwo} may
impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} depicts a scenario comprising only three
\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
receive the messages in the order of their sending ($s_{pq}(m)
\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB}, both $a$ and $c$ delete their partition
while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, $b$ receives, delivers, and forwards
$\alpha_c^1$, for it improves its best partition. Then it receives and
discards $\delta_a$, for its best partition does not match the deleted
one. We simplify the echo since $\alpha_c^3$ is already transiting
towards $a$. Finally, Figure~\ref{fig:problemD} shows that eventually,
$c$ stays in the deleted partition $P_a$ for not having received
$\delta_a$ that $b$ blocked earlier. The system does not reach
consistent partitioning. \end{proof}

As a cascading effect, in Figure~\ref{fig:problemD}, not only $c$
wrongfully believes that it belongs to $a$'s partition when $a$
already deleted it, but it could contribute to its inconsistency by
blocking farther but up-to-date messages from actual sources. To reach
consistent partitioning, \processes need
\begin{inparaenum}[(i)]
\item to detect possibly blocking conditions 
\item to purge all stale messages from the system
\item enabling up-to-date notifications to eventually echo back to
  every \process.
\end{inparaenum}

\begin{lemma}[\label{def:detection}\underline{D}etector existence (D)]
  Assuming a chain of \processes $[x,\ldots, z]$ that delivered a
  message $\alpha_x$, when $x$ deletes its partition, either every
  \process of this chain eventually deliver $\delta_s$, or a \process
  along the chain detects the blocking of the staleness notification
  $\delta_s$.
\end{lemma}

\begin{proof}
  \TODO{Rework this!} We must prove that every \process that delivered
  a stale $\alpha_X$ eventually delivers a better $\alpha_Y$, or
  delivers a removal notification of $\alpha_X$.
  Figure~\ref{fig:proofB} summarizes the issue of purging in scenarios
  involving concurrent operations.

  (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
  but whose parent is neither inconsistent (like $b$) nor receiving
  $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
  \process, either directly or transitively, for such a child \process
  ($d$) trusts the possible removal of $P_X$ by delivering and
  forwarding such $\Delta$. $\Delta$ suffers from identical blocking
  conditions (between $b$ and $c$) than $\delta$, leading to the same
  solutions of detection and propagation of $\Delta$. Eventually,
  every \process whose last delivery is $\alpha_X$ receives and
  delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
\end{proof}

To reach dynamic consistent partitioning, the detecting \process must
broadcast a message notifying the \emph{possible} staleness of its
last delivered and forwarded message to its \emph{downstream}
\processes. Indeed, Figure~\ref{fig:undoproblem} shows that from
detector's perspective, the chain of events is identical, yet it must
react to the worst case scenario where $\delta_a$ existed and was
blocked. \TODO{More about figure.} \TODO{Challenging?}

\begin{definition}[FS$^+$: forwarding staleness downstream]
  To further reduce the scope  \TODO{Meow.}
\end{definition}

\begin{theorem}[$\textup{FB}^+ \wedge \textup{FS}^+ \wedge \textup{D} \implies \textup{DCP}$]
  \TODO{Miaw}
\end{theorem}

\begin{proof}
  \TODO{Meow.}
\end{proof}

%% \begin{definition}[\label{def:purge}Message purge]
%%   A system \underline{p}urges a message when every \node $q$ that
%%   delivered $m$ eventually delivers another message $m'$ never
%%   followed by the delivery of the former message $m$:
%%   $d_q(m) \implies \exists m': \eventually (d_q(m) \rightarrow d_q(m')
%%   \wedge \neg (d_q(m') \rightarrow d_q(m)))$.
%% \end{definition}

%% \begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
%%     \underline{D}ynamic \underline{c}onsistent
%%     \underline{p}artitioning (DCP)]
%% %
%%   When a \process can \texttt{Add} and \texttt{Del}ete its partition,
%%   to ensure consistent partitioning, eventual forwarding of best
%%   (Theorem~\ref{theo:efb}) additionally requires
%% \begin{inparaenum}[(i)]
%% \item eventual purging of stale messages ($\mathcal{S}(m) \implies
%%   \mathcal{P}(m)$), then
%% \item the eventual forwarding of best (Theorem~\ref{theo:efb}).
%% \end{inparaenum}
%% \end{theorem}

%% \begin{proof}
%%   %% To reach consistent partitioning, the last message delivered by
%%   %% every process is not stale and comes from its respective best
%%   %% source: $d(m)$
%%   Assuming EFB as default propagation behavior where \processes
%%   deliver and forward the best sum of weights they received. We must
%%   prove that despite stale messages, the last delivery of every
%%   \process is the message that followed the shortest path to its
%%   closest source.
%%   \begin{asparadesc}
%%   \item [EFB without Purge:] A \process may receive messages in such
%%     an order (\eg in Figure~\ref{fig:problemC}: $d_b(\alpha_c^1)
%%     \rightarrow r_b(\delta_a) \rightarrow r_b(\delta_a)$) that it does
%%     not forward messages required by other \processes ($\delta_a$ for
%%     $c$). The last delivery of some nodes may be wrong (\eg in
%%     Figure~\ref{fig:problemD}: $\alpha_a^3$ instead of $\delta_a$).
%%     % \Processes never
%%     % reach consistent partitioning.
%%     %
%%     %% Figure~\ref{fig:proofA} depicts the generic case where a \process
%%     %% $b$ precludes itself and subsequent \processes such as $c$ of
%%     %% delivering the message from their respective best source
%%     %% $a$. \Process $b$ received and delivered a message from a
%%     %% partition that has since then been deleted but with a better sum
%%     %% of weights than newly received ones ($\alpha_d^y <
%%     %% \alpha_a^{x'}$). It forever discards such a message
%%     %% $\alpha_a^{x'}$.
%%   \item [Purge not followed by EFB:]
%%     %% also transiting messages
%%     Assuming that every \process removes control information as soon
%%     as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
%%     \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
%%     anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
%%     \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
%%     up-to-date messages propagation. However, even in such settings,
%%     depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
%%     r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
%%     may never receive again, hence deliver and forward a message that
%%     was received and discarded before ($\alpha_c^{y}$). When such a
%%     message contains its best up-to-date partition, a \process may
%%     never end up in its best partition.
%%     %    Therefore, \processes do not reach
%%     % consistent partitioning.
%%   \item [Purge then EFB:] Assuming the eventual and definitive removal
%%     of stale messages at each \process ($S(\alpha_a) \implies
%%     (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
%%     d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
%%     removal eventually triggers the forwarding of best delivered
%%     messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
%%     \processes may deliver other stale messages that will be 
%%     eventually removed to never be delivered again. In the worst case,
%%     all \processes deliver and remove all stale messages to ultimately
%%     deliver and forward only up-to-date messages ($\eventually d_c(m')
%%     \implies \neg S(m')$). As in Theorem~\ref{theo:efb}, they
%%     eventually deliver and forward their best up-to-date message.

%%     %% upon receipt of such $\alpha_y$, either the \process already
%%     %% delivered its removal and it does

%%     %% ($d_c(\delta_x) \implies \eventually f_d(\alpha_y) \wedge \neg
%%     %% S(\alpha_y)$)

%%     %% eventually every \process only delivers and forwards up-to-date
%%     %% messages, or no message at all

%%     %% , every \process eventually delivers and forwards the best
%%     %% up-to-date delivered messages as in Theorem~\ref{theo:bef}.

%%     %% Removing \emph{forever} all such stale messages about
%%     %% deleted partitions would allow \processes to propagate their best
%%     %% up-to-date partition again, eventually reaching consistent
%%     %% partitioning together, as stated by Theorem~\ref{theo:bef}.
%%   \end{asparadesc}
%%   Using EFB$^+$, \processes reach consistent partitioning together
%%   even under dynamic partitioning settings where \nodes can
%%   \texttt{Add} and \texttt{Del}ete their partition.
%% \end{proof}

@@

%% The main challenge consists in implementing a purging mechanism that
%% ensures the \emph{eventual and definitive} removal of stale control
%% information.
%% One could guarantee consistent partitioning by always
%% propagating the $\delta$ messages corresponding to the $\alpha$
%% messages it propagated before. In Figure~\ref{fig:problem}, it means
%% that as soon as \Process~$b$ forwards $\alpha_a^2$, it assumes that
%% its neighbors \Process~$c$ and \Process~$d$ may need the notification
%% of removal $\delta_a$ if it exists. However, such a solution also
%% implies that \processes generate traffic not only related to their
%% current partition, but also related to partitions they belonged to in
%% the past. This would prove overly expensive in dynamic systems where
%% \processes join and leave the system, create and delete partitions, at
%% any time.  Instead, we propose to use the delivery order at each
%% \process to detect possible inconsistencies and solve them.
%% Together, \processes eventually remove all stale control information
%% (transiting messages and local states) of the system leaving room for
%% propagation of messages about up-to-date partitions.

@@

%% \begin{theorem}[\label{theo:threephase}Three-phase purge]
%%   Three phases are sufficient to eventually purge the system from
%%   stale control information:
%%   \begin{inparaenum}[(i)]
%%   \item propagation of delete notifications,
%%   \item detection of possibly blocked deletion, and
%%   \item propagation of delete notifications that were possibly blocked.
%%   \end{inparaenum}
%% \end{theorem}

@@

%% \begin{proof}
%%   We must prove that every \process that delivered a stale $\alpha_X$
%%   eventually delivers a better $\alpha_Y$, or delivers a removal
%%   notification of $\alpha_X$.  Figure~\ref{fig:proofB} summarizes the
%%   issue of purging in scenarios involving concurrent operations.

%%   (i) If every \process (such as $a$) starting from the source
%%   delivers and forwards a removal notification $\delta_X$ when their
%%   last delivery is $\alpha_X$, then every such \process eventually
%%   delivers the removal notification $\delta_X$ except \processes (such
%%   as $b$) that delivered $\alpha_X$ from a \process that delivered a
%%   message from another partition $\alpha_Y$ since then.

%%   These exceptions eventually receive and deliver $\alpha_Y$ since
%%   $\alpha_Y$ is better than $\alpha_X$ through this path, except if
%%   they already received and delivered the removal notification of
%%   $P_Y$ (such as $c$). These \processes may never receive hence
%%   deliver $\delta_X$, and may never receive hence deliver a better
%%   message than $\alpha_X$. They need an additional mechanism to
%%   eventually purge $\alpha_X$ that cannot rely on the eventual purging
%%   of $P_Y$ at \processes like $b$, to avoid deadlocks.

%%   (ii) Assuming that every \process keeps an history of its past
%%   deliveries, \processes (such as $c$) can detect the inconsistency,
%%   since they receive from their parent an already deleted partition
%%   $P_Y$. This notification means that the parent discards any
%%   $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
%%   $\delta_X$ exists, it discards it. To ensure the purge of stale
%%   messages, a detecting \process must assume the worst case that such
%%   $\delta_X$ exists, and send another kind of message, noted $\Delta$,
%%   that notify the possible removal of $P_X$.

%%   (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
%%   but whose parent is neither inconsistent (like $b$) nor receiving
%%   $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
%%   \process, either directly or transitively, for such a child \process
%%   ($d$) trusts the possible removal of $P_X$ by delivering and
%%   forwarding such $\Delta$. $\Delta$ suffers from identical blocking
%%   conditions (between $b$ and $c$) than $\delta$, leading to the same
%%   solutions of detection and propagation of $\Delta$. Eventually,
%%   every \process whose last delivery is $\alpha_X$ receives and
%%   delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
%%   %
%%   %% Some \processes may have delivered messages about other partitions
%%   %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
%%   %% messages about $P_Y$.  For \processes such as $b$, the last delivery
%%   %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
%%   %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
%%   %% as $c$, the last delivery is $\alpha_X$, and they delivered the
%%   %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
%%   %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
%%   %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
%%   %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
%%   %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
%%   %% the chain: $d$ is a child of \processes that delivered messages
%%   %% about $P_Y$.
%%   %
%%   %% \begin{asparadesc}
%%   %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
%%   %%   like $a$.  By propagating from \process to \process the
%%   %%   corresponding $\delta_X$ message, these \processes purge
%%   %%   $\alpha_X$.
%%   %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
%%   %%   latter does not target its current partition.
%%   %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
%%   %%   that $[a, b, c, d]$ is solved and that it does not require to
%%   %%   purge $P_Y$.}
%%   %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
%%   %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
%%   %%   it detects $b$ is its parent, and possibly blocked any delta with
%%   %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
%%   %%   sure, $\Delta$
%%   %
%%   %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
%%   %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
%%   %%   \Process~$b$ that do not directly suffer from the non-delivery of
%%   %%   $\delta_X$. They need to purge their own $P_Y$ if need
%%   %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
%%   %%   one following \process will receive.
%%   %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
%%   %%   such as \Process~$c$ that do not belong to the preceding category,
%%   %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
%%   %%   forwarding guarantees that they receive $\alpha_Y$, which
%%   %%   contradicts their history or state. In such a case, the detecting
%%   %%   \processes purge their own $\alpha_X$. The detecting \processes
%%   %%   must also notify subsequent \processes that their current
%%   %%   partition \emph{may be} deleted. Indeed their parent may have
%%   %%   blocked the corresponding $\delta$ messages and subsequent
%%   %%   \processes must purge their possibly stale state, for the sake of
%%   %%   consistency.  We note such a notification $\Delta_X$ to emphasize
%%   %%   their proximity to $\delta_X$ messages.
%%   %%   % the uncertainty of a $\delta$ message.
%%   %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
%%   %%   their parent:] \Processes such as \Process~$d$ that have
%%   %%   $\alpha_X$ but preceding delivered messages are not
%%   %%   important. Such \processes must trust detecting \processes by
%%   %%   delivering and forwarding $\Delta_X$. It is worth noting that
%%   %%   these messages are subject to all aforementioned blocking
%%   %%   conditions, but are also solved by aforementioned mechanisms.
%%   %% \end{asparadesc}
%%   %% Propagation~I terminates: a \process does not deliver a $\delta$
%%   %% message if it has already delivered it. Propagation~III terminates: a
%%   %% \process does not deliver a looping message.  
%%   % ; and since \processes forward the messages they deliver, upstream
